SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-19 paper/encoding.tex
changes

In this section, we will present our encoding of the search problem. Every variable is a Boolean bit, for example, n(0,1) represents node 0 with type 1 molecule present. Assignment to the Boolean variable n(0,1) to True will mean that at node 0 type 1 molecule is present.

>>>>

In this section, we will formally define VTSs as a labelled graph
and the conditions on the graphs that are discussed in the previous
section.
Subsequently, we will present the SAT encoding of the search problems
for the graphs that satisfies the conditions.

\subsection{Model}

We model VTSs as labelled directed graphs.
The graph labels both edges and labels with sets of molecules to denote
the set of molecules present in the node.
The graph is formally defined as follows.

\begin{df}
  A VTS $G$ is tuple $(\nodes,\mols,\edges,\nlabel,\pair,\edgef,\nodef)$, where
  \begin{itemize}
  \item $\nodes$ is a set of nodes representing compartments in the VTS,
  \item $\mols$ is the set of molecules flowing in the network, 
  \item $\nlabel : \nodes \maps \powerset{\mols}$ defines the molecules present in the nodes  
  \item $ \nodes \times \powerset{\mols} \times \nodes \subseteq \edges$ is the set of edges
    with molecule sets as labels
  \item $\pair : \mols \times \mols$ is pairing relating
  \item $\nodef : \mols \maps \powerset{\mols} \maps \booleans$ is activity maps for nodes
  \item $\edgef : \mols \maps \powerset{\mols} \maps \booleans $ is activity maps for edges
  \end{itemize}
\end{df}
$\pair$, $\nodef$, and $\edgef$ defines activity of a molecule on nodes and edges.
A molecule $k$ is {\em active} at node $n$ if $\nodef(k,\nlabel(n))$ is true.
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $\edgef(k,M')$ is true.

Variants of the model : restrictions...

formal definition of the properties in the terms of VTS.

State the SAT problem

\subsection{Boolean satisfiability of the problem}

Every variable is a Boolean bit, for example, n(0,1) represents node 0 with type 1 molecule present. Assignment to the Boolean variable n(0,1) to True will mean that at node 0 type 1 molecule is present.
